---
title: "Netflix Data Analysis"
author: "Nina Austria"
date: "9/25/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE) # hiding all warnings and messages
```

### Reading in Our Dataset:
```{r}
library(readxl)

netflix = read.csv("netflix_titles.csv")
```

### Installing Libraries:
```{r}
library(tidyverse)
library(readr)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(naniar)
library(forcats)
library(wordcloud)
library(tm)
library(SnowballC)
library(RColorBrewer)
library(tidytext)

# glimpse(netflix)
# summary(netflix)
```

### Going through dataset and looking for any inconsistencies -- are there missing values, weird capitalizations, inconsistent units?
Want to separate the 'date_added' var into 2 columns: month/day and year:
```{r}
netflix = netflix %>% separate(date_added, c("date_added", "year_added"), sep = ",") # use arrow pointing down, next to green arrow to undo the run
```

Want to separate the 'listed_in' var into 3 columns:
```{r}
netflix = netflix %>% separate(listed_in, c("Category1", "Category2", "Category3"), sep = ",") 
```

### Country Column Analysis
Want to convert blank spaces to NAs and count the number of missing values in the variable 'country':
```{r}
netflix = netflix %>% mutate_all(na_if, "")

netflix %>% count(is.na(netflix$country), sort = TRUE)

country <- drop_na(netflix, country)
```

```{r}
country %>% group_by(country) %>% count(country, type) %>% arrange((desc(n))) %>% head(25) # count(country,type) means there will be sep rows for United States - Movie and United States - TV Show
```

# Data Visualization

### Netflix Movies and TV Shows Over the Years:
```{r}
ggplot(data = netflix, mapping = aes(x = release_year, fill = type)) +
  geom_histogram(color = "black", binwidth = 2) + 
  labs(title = "Release by Year")
```

See how many values in country column are NA (missing) and drop the missing values, save in new dataset:
```{r}
netflix %>% count(is.na(country), sort = TRUE)

country_release <- drop_na(netflix, country)

country_release %>% 
  count(country, sort = TRUE) %>% 
  group_by(country) %>%
  head(25) %>% 
  ggplot(mapping = aes(x = reorder(country, n), y = n, fill = country)) + 
  geom_col(show.legend = FALSE) + 
  labs(x = "Sum of Movies & TV Shows Frequency", y = "Movies and TV Shows Released", title = "Top 25 Countries on Netflix") + 
  coord_flip() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) + # he just copied and pasted this from somewhere 
  geom_label(mapping = aes(label = n), show.legend = FALSE) + 
  scale_y_continuous(expand = c(0,0), limits = c(0,3000))
```

These next two visualizations are from Kaggle (General tip: if we want to see nice visualizations for code, go to Kaggle -> Netflix Dataset -> Code -> filter by R -> find visuals/tables you find interesting and want to copy + paste into your project):

### Graph: Rating by Type
```{r}
netflix %>%
 filter(!(rating %in% c("74 min", "84 min", "66 min", ""))) %>%
 ggplot() +
  aes(x = rating, fill = rating) +
  geom_bar() +
  scale_fill_hue(direction = 1) +
  labs(x = "Rating", y = "Count", title = "Rating by Type") +
  theme_minimal() +
  facet_wrap(vars(type)) +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

### Word Cloud!
```{r}
desc_words_m <- netflix %>% select(type, show_id, description) %>%
  filter(type == "Movie") %>% 
    unnest_tokens(word, description) %>%
    anti_join(stop_words)
count_word <- desc_words_m %>%
   count(word, sort = TRUE)
wordcloud(words = count_word$word,  
          freq = count_word$n, 
          min.freq = 50,  
          max.words = nrow(count_word), 
          random.order = FALSE,  
          rot.per = 0.1,  
          colors = brewer.pal(8, "Dark2"))
```
